A supertree pipeline for summarizing phylogenetic and taxonomic information for millions of species

### 2017-01-25 doc/paper1-submission/paper5-adjusted.tex
Convert figures 11-13

\begin{centering}
\includegraphics[scale=0.5]{Figures__labelled_supertree__labelled_supertree_only_taxon_names\lyxdot tre}
\par\end{centering}
\caption{\label{fig:unprune}Unpruned tree with internal taxa. Taxa unsampled in phylogenetic
statements have been added to the grafted tree shown
in Fig. \ref{fig:grafted-solution}.}
\end{figure}

\begin{figure}
\begin{centering}
\subfloat[Taxonomy]{\begin{centering}
\begin{minipage}[c][1\totalheight][t]{0.45\columnwidth}%
\begin{center}
\includegraphics[scale=0.38]{example3__cleaned_ott-labels\lyxdot tre}
\par\end{center}%
\end{minipage}
\par\end{centering}
}\hfill{}\subfloat[Grafted solution]{\begin{centering}
\begin{minipage}[c][1\totalheight][t]{0.45\columnwidth}%
\begin{center}
\includegraphics[scale=0.38]{example3__grafted_solution-labels\lyxdot tre}
\par\end{center}%
\end{minipage}
\par\end{centering}
}\hfill{}
\par\end{centering}
\begin{centering}
\subfloat[Unpruned tree - broken taxa removed]{\begin{centering}
\includegraphics[scale=0.38]{example3__unprune-old-labels\lyxdot tre}
\par\end{centering}
}\hfill{}\subfloat[Unpruned tree with MRCA-attachment]{\begin{centering}
\includegraphics[scale=0.38]{example3__unprune-new-labels2\lyxdot tre}
\par\end{centering}
}
\par\end{centering}
\caption{\label{fig:Two-approaches-to-unpruning}Two approaches to unpruning.
Taxa G and R in the taxonomy (a) are broken because they conflict
with the grafted solution (b). Removing these broken taxa from the
taxonomy before unpruning leads to taxa R4, R5, and R6 being attached
directly at taxon N, as in tree (c). In tree (d), the children of
the broken taxon R are instead attached at the MRCA of R1, R2, and
R3. Our method follows the second approach.}
\end{figure}

@@

\begin{figure}
\subfloat[Input tree $T_{1}$ named ``tree1'']{%
\begin{minipage}[c][1\totalheight][t]{0.25\columnwidth}%
\includegraphics[scale=0.5]{annotation_example__input1\lyxdot tre}%
\end{minipage}

}\hfill{}\subfloat[Summary Tree $\protect\summaryTree$]{%
\begin{minipage}[c][1\totalheight][t]{0.35\columnwidth}%
\includegraphics[scale=0.5]{annotation_example__summary\lyxdot tre}%
\end{minipage}

}\hfill{}\subfloat[Induced Tree $\protect\summaryTree(1)$]{%
\begin{minipage}[c][1\totalheight][t]{0.35\columnwidth}%
\includegraphics[scale=0.5]{annotation_example__induced1_color}%
\end{minipage}

@@

\hfill{}\subfloat[JSON annotations relating edges of (c) to edges of (a)]{%
\shadowbox{\begin{minipage}[t]{1.0\columnwidth}%
\texttt{\{}

\texttt{~~\textquotedbl{}nodes\textquotedbl{}: \{}

\texttt{~~~~\textquotedbl{}mrcaott1ott4\textquotedbl{}: \{ \textquotedbl{}}\texttt{\textcolor{blue}{partial\_path\_of}}\texttt{\textquotedbl{}: \{
\textquotedbl{}tree1\textquotedbl{}: \textquotedbl{}node15\textquotedbl{},
... \} \},}

\texttt{~~~~\textquotedbl{}ott10\textquotedbl{}:~~~~~~~~~\{
\textquotedbl{}}\texttt{\textcolor{blue}{partial\_path\_of}}\texttt{\textquotedbl{}: \{
\textquotedbl{}tree1\textquotedbl{}: \textquotedbl{}node15\textquotedbl{},
... \} \},}

\texttt{~~~~\textquotedbl{}mrcaott5ott7\textquotedbl{}: \{ \textquotedbl{}\textcolor{mylime}{supported\_by}\textquotedbl{}:~~~
\{ \textquotedbl{}tree1\textquotedbl{}: \textquotedbl{}node16\textquotedbl{},
... \} \},}

\texttt{~~~~\textquotedbl{}ott1\textquotedbl{}:~~~~~~~~~~\{
\textquotedbl{}}\texttt{\textcolor{orange}{terminal}}\texttt{\textquotedbl{}: ~~~~~~~\{
\textquotedbl{}tree1\textquotedbl{}: \textquotedbl{}ott1\textquotedbl{},
... ~~\} \},}

\texttt{~~~~\textquotedbl{}ott2\textquotedbl{}:~~~~~~~~~~\{
\textquotedbl{}}\texttt{\textcolor{orange}{terminal}}\texttt{\textquotedbl{}: ~~~~~~~\{
\textquotedbl{}tree1\textquotedbl{}: \textquotedbl{}ott2\textquotedbl{},
... ~~\} \},}

\texttt{~~~~\textquotedbl{}ott5\textquotedbl{}:~~~~~~~~~~\{
\textquotedbl{}}\texttt{\textcolor{orange}{terminal}}\texttt{\textquotedbl{}: ~~~~~~~\{
\textquotedbl{}tree1\textquotedbl{}: \textquotedbl{}ott5\textquotedbl{},
... ~~\} \},}

\texttt{~~~~\textquotedbl{}ott11\textquotedbl{}:~~~~~~~~~\{
\textquotedbl{}}\texttt{\textcolor{orange}{terminal}}\texttt{\textquotedbl{}: ~~~~~~~\{
\textquotedbl{}tree1\textquotedbl{}: \textquotedbl{}ott5\textquotedbl{},
... ~~\} \},}

\texttt{~~~~\textquotedbl{}ott7\textquotedbl{}:~~~~~~~~~~\{
\textquotedbl{}}\texttt{\textcolor{orange}{terminal}}\texttt{\textquotedbl{}: ~~~~~~~\{
\textquotedbl{}tree1\textquotedbl{}: \textquotedbl{}ott7\textquotedbl{},
... ~~\} \}}

\texttt{~~\},}

\texttt{~~...}

\texttt{\} }%
\end{minipage}}

>>>>

\begin{centering}
\includegraphics[scale=0.5]{Fig11}
\par\end{centering}
\caption{\label{fig:unprune}Unpruned tree with internal taxa. Taxa unsampled in phylogenetic
statements have been added to the grafted tree shown
in Fig. \ref{fig:grafted-solution}.}
\end{figure}

\begin{figure}
\begin{centering}
\subfloat[Taxonomy]{\begin{centering}
\begin{minipage}[c][1\totalheight][t]{0.45\columnwidth}%
\begin{center}
\includegraphics[scale=0.38]{Fig12a}
\par\end{center}%
\end{minipage}
\par\end{centering}
}\hfill{}\subfloat[Grafted solution]{\begin{centering}
\begin{minipage}[c][1\totalheight][t]{0.45\columnwidth}%
\begin{center}
\includegraphics[scale=0.38]{Fig12b}
\par\end{center}%
\end{minipage}
\par\end{centering}
}\hfill{}
\par\end{centering}
\begin{centering}
\subfloat[Unpruned tree - broken taxa removed]{\begin{centering}
\includegraphics[scale=0.38]{Fig12c}
\par\end{centering}
}\hfill{}\subfloat[Unpruned tree with MRCA-attachment]{\begin{centering}
\includegraphics[scale=0.38]{Fig12d}
\par\end{centering}
}
\par\end{centering}
\caption{\label{fig:Two-approaches-to-unpruning}Two approaches to unpruning.
Taxa G and R in the taxonomy (a) are broken because they conflict
with the grafted solution (b). Removing these broken taxa from the
taxonomy before unpruning leads to taxa R4, R5, and R6 being attached
directly at taxon N, as in tree (c). In tree (d), the children of
the broken taxon R are instead attached at the MRCA of R1, R2, and
R3. Our method follows the second approach.}
\end{figure}

@@

\begin{figure}
\subfloat[Input tree $T_{1}$ named ``tree1'']{%
\begin{minipage}[c][1\totalheight][t]{0.25\columnwidth}%
\includegraphics[scale=0.5]{Fig13a}%
\end{minipage}

}\hfill{}\subfloat[Summary Tree $\protect\summaryTree$]{%
\begin{minipage}[c][1\totalheight][t]{0.35\columnwidth}%
\includegraphics[scale=0.5]{Fig13b}%
\end{minipage}

}\hfill{}\subfloat[Induced Tree $\protect\summaryTree(1)$]{%
\begin{minipage}[c][1\totalheight][t]{0.35\columnwidth}%
\includegraphics[scale=0.5]{Fig13c}%
\end{minipage}

@@

\hfill{}\subfloat[JSON annotations relating edges of (c) to edges of (a)]{%
\includegraphics{Fig13d}%
}\hfill{}
